Implicit assumptions and their impact on photometric redshift PDF performance in the context of LSST

### 2018-12-13 paper/main.tex
add funding source

In order to maximize scientific returns of current and upcoming galaxy surveys, the photometric redshift (photo-$z$) posterior distributions produced by redshift estimation codes must be accurate probability distribution functions (PDFs).  However, the posteriors resulting from a number of current techniques are not, in general, consistent with each other, affected by implicit assumptions made by each code, and an optimal method for obtaining an accurate PDF estimate remains unclear.   We present the results of an initial study of the Large Synoptic Survey Telescope Dark Energy Science Collaboration (\textsc{LSST-DESC}) testing twelve photo-$z$ algorithms using complete and representative training data and evaluate multiple metrics to test how accurately the posteriors represent probability distributions.  We observe several trends, including systematic biases and an overall over/under-prediction in the broadness of the PDFs in many of the codes which may be symptomatic of implementation problems or problems in underlying algorithm design.  A careful accounting of all systematics discovered will be necessary for the codes employed in upcoming analyses in order to achieve unbiased cosmological measurements.

@@

{ \red{personal funding sources}}

AIM is advised by David W. Hogg and was supported by National Science Foundation grant AST-1517237.

>>>>

In order to maximize scientific returns of current and upcoming galaxy surveys, the photometric redshift (photo-$z$) posterior distributions produced by redshift estimation codes must be accurate probability distribution functions (PDFs).  However, the posteriors resulting from a number of current techniques are not, in general, consistent with each other, affected by implicit assumptions made by each code, and an optimal method for obtaining an accurate PDF estimate remains unclear.   We present the results of an initial study by the Large Synoptic Survey Telescope Dark Energy Science Collaboration (\textsc{LSST-DESC}) testing twelve photo-$z$ algorithms using complete and representative training data and evaluate multiple metrics to test how accurately the posteriors represent probability distributions.  We observe several trends, including systematic biases and an overall over/under-prediction in the broadness of the PDFs in many of the codes which may be symptomatic of implementation problems or problems in underlying algorithm design.  A careful accounting of all photo-$z$ systematics will be necessary for the codes employed in upcoming analyses in order to achieve unbiased cosmological measurements.

@@

{ \red{personal funding sources}}
S.~Schmidt acknowledges support from DOE grant DE-SC0009999 and NSF/AURA grant N56981C.  AIM is advised by David W. Hogg and was supported by National Science Foundation grant AST-1517237.
